---
title: "Speeding on the A13"
author: "Rudy Veenhoff"
date: "12 december 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- A13 is an important motorway connecting The Hague and Rotterdam.
- In 2011 TNO conducted a research on the traffic on this highway.
- Numbers of cars per minute (flow) as well as average speed were measured using "loops" placed inside the road.
- We will look at the average speed of the traffic along the highway at a given day.

```{r setting up, cache=TRUE}
setwd("~/Rudy/Data Science/Projects/Developing Data Products/PA2")
rechtsSpeed <- read.csv("Rechts_Speed_2011.csv")
colnames <- gsub("^X","",colnames(rechtsSpeed))
order<-order(as.numeric(colnames))
SpeedOrdered <- rechtsSpeed[order]

is.wholenumber <-  function(x, tol = .Machine$double.eps^0.5){  
  abs(x - round(x)) < tol
}

dayOfYear <- function(n){
  if(n >=1 && n <= 365 && is.wholenumber(n)){
    beginofday <- (n-1)*60*24
    endofday <- n*60*24-1
    SpeedOrdered[beginofday:endofday,]
  }
  else
    stop("Please enter an integer between 1 and 365")
}

fullNameOfDay <- function(n){
  Sys.setlocale("LC_TIME", "English")
  daysof2011 <- seq(as.POSIXct("2011/1/1"),as.POSIXct("2011/12/31"),"day")
  format(daysof2011[n],"%A %d %B %Y")
}

plotHeatmap <- function(n){
  library(plotly)
  
  x <- list(
    title = "The 143 measurement points on the A13"
  )
  
  y <- list(
    title = "Minutes past midnight"
    )
  
  z <- dayOfYear(n)
  
  p <- plot_ly(z=as.matrix(dayOfYear(n)),
               type="heatmap") %>% 
    colorbar(title = "Speed in km/h") %>%
    layout(title = fullNameOfDay(n), xaxis = x, yaxis=y)
  p
}
```



## Introduction part 2

- The data shown is from the traffic coming from The Hague and going to Rotterdam.
- There were 143 points of measurement along this side of the A13.




## Heatmap
```{r heatmap, message=FALSE, comment=FALSE, warning=FALSE}
plotHeatmap(12)
```

## Try it yourself!
If you want to make heatmaps for other days yourself, check out my github account (github.com/RudyVeenhoff) for the code.


